Bayesian Sparsification of $\cplx$-valued networks

### 2019-11-21 paper/paper.tex
some intro on dropout: used srivastava-et-al and wang-manning

Deep neural networks are an integral part of machine learning and data science toolset
for practical data-driven problem solving. Despite recent advances in generalization
and optimization theory specific to deep networks, deploying in actual embedded hardware
remains a challenge. Solving the storage and compute constraints encourages development
of model compression and sparsification methods, that focus on favourable tradeoff between
performance and size. Most popular techniques include weight pruning \citep{citation_needed},
model quantization from IEEE754 floating point to integer-based arithmetic \citep{citation_needed},
and dropout. The key assumption is that the more explicitly zero parameters there is,
the less computations is needed.

Bayesian Inference is a principled framework of reasoning about uncertainty. The core principle
is updating prior beliefs in accordance with the likelihood of empirical observations into
posterior belief. Under suitable modelling and prior assumptions, Bayesian methods can be
used towards model sparsification, \citep{kingma_variational_2015,molchanov_variational_2017},
and \citep{kharitonov_variational_2018}.

>>>>

% general intro text with motivation
Deep neural networks are an integral part of machine learning and data science toolset
for practical data-driven problem solving. Despite recent advances in generalization
and optimization theory specific to deep networks, deploying in actual embedded hardware
remains a challenge. Solving the storage and compute constraints encourages development
of model compression and sparsification methods, that focus on favourable tradeoff between
performance and size. Most popular techniques include weight pruning \citep{citation_needed},
model quantization from IEEE754 floating point to integer-based arithmetic \citep{citation_needed},
and dropout. The key assumption is that the more explicitly zero parameters there is,
the less computations is needed.

% on dropout
Dropout, \citep{hinton_improving_2012}, prevents overfitting by injecting multiplicative
binary noise into layer's weights, thereby breaking up co-adaptations that could occur
during training. \citet{wang_fast_2013} argue that the overall effect of binary dropout
on the intermediate outputs via the Central Limit Theorem can be approximated by a Gaussian
with weight-input dependent mean and variance. \citet{srivastava_dropout_2014} propse
using independent $\mathcal{N}(1,1)$ noise, arguing that higher entroy of a Gaussian has
better regularizing effect. In multitask learning \citet{cheung_superposition_2019}
has shown the possiblity of storing task-specific parameters in non-destructive superposition
within a single network. Their argument implies that if the single task setting is viewed
as replicated mutlitask learning, then by sampling uncorrelated weight masks dropout acts
as superposition method, which better utilizes the learnig capacity of the network.
% many identical copies of the same task; \cite[Appendix A.1]{cheung_superposition_2019}

% segue into bayesian inference
Dropout resembles averaging models with shared parameters: each model is weighted equally
since masks are randomly sampled, unlike bayesian model averaging, which weighs accoring to
the posterior distribution. \citet{kingma_variational_2015} specifically consider dropout
as a Bayesian inference technique. Bayesian Inference as a principled framework of reasoning
about uncertainty, updates prior beliefs in accordance with the likelihood of empirical
observations into posterior belief. Under suitable modelling and prior assumptions, Bayesian
methods can be used towards model sparsification, \citep{kingma_variational_2015,molchanov_variational_2017},
and \citep{kharitonov_variational_2018}.
